---
title: "Method comparision"
author: "Alexander Schwaiger"
date: "2023-01-20"
output: pdf_document
---
```{r eval=FALSE, message=FALSE, warning=FALSE}
source("dependencies.R")
source("coda_functions.R") 
source("ingarch_functions.R")
source("general_helper_functions.R")
```


Plot parameters 
```{r eval = FALSE}
text_size <- 50
save_plots <- T
```


Preparation
```{r eval = FALSE}
ids <- c(4,6)
prediction_error_step <- 1
frame <- 5
window_method <- "extending"
save_results <- T

#Ingarch specifications
distr<-"poisson"
zero_handling_ingarch <- "zero_to_one"
external <- F
if(external){
  external_plot <-"with external factors"
}else external_plot <- ""
past_means <- c(1)
past_obs <- c(1)
ingarch_settings <- expand_grid(past_means,past_obs)


#Coda specifications
zero_handling_coda<-"all"
tspace<-T
take_log<-T
one_vs_all<-T
```


Performing the Analysis
```{r eval=FALSE, include=FALSE}
coda_result <-
  coda.analysis(
    weekly_category_data = weekly_category_data,
    ids = ids,
    frame = frame,
    one_vs_all = one_vs_all,
    pivot_groups = c("1", "2", "3", "4"),
    tspace = T,
    take_log = T,
    zero_handling = zero_handling_coda,
    window_method = window_method
  )

if(save_results){
  save(coda_result,file=here("Code/results",paste("coda_result_ids",paste(ids,collapse="-"),"win_lgth",frame,".RData",sep="")))
}




for (i in 1:dim(ingarch_settings)[1]){
  
  past_obs <- ingarch_settings[[i,2]]
  past_mean <- ingarch_settings[[i,1]]
  
  ingarch_result <-
  ingarch.analysis(
    weekly_category_data = weekly_category_data,
    ids = ids,
    frame = frame,
    distribution = distr,
    categories = c("1","2","3","4"),
    window_method = window_method,
    zero_handling = zero_handling_ingarch,
    external = external,
    multicore = T,
    n_cores = 3,
    past_obs = past_obs,
    past_mean = past_mean
  )
  
  if(save_results){
  save(ingarch_result,file=here("Code/results",paste("ingarch_result_ids",paste(ids,collapse="-"),"_ext","_",external,
                                             "win_lgth",frame,"_pobs",past_obs,"_pmeansu",past_mean,".RData",sep="")))
}
}


```

Loading previous results
```{r eval=FALSE, include=FALSE}
ids <- unique(coda_result$results$id)
prediction_error_step <- 1
frame <- unique(coda_result$results$window_length_base)
window_method <- unique(coda_result$results$window_method)
save_results <- T

#Ingarch specifications
distr<-unique(ingarch_result$results$distribution)
zero_handling_ingarch <- unique(ingarch_result$results$zero_handling)
external <- unique(ingarch_result$results$external)
if(external){
  external_plot <-"with external factors"
}else external_plot <- ""
past_means <- unique(ingarch_result$results$past_mean)
past_obs <- unique(ingarch_result$results$past_obs)
ingarch_settings <- expand_grid(past_means,past_obs)


#Coda specifications
#zero_handling_coda<-unique(coda_result$results$zero_handling)
tspace<-T
take_log<-T
one_vs_all<-T

if(!identical(ids,unique(ingarch_result$results$id)) || 
   frame != unique(ingarch_result$results$window_length_base) ||
   window_method != unique(ingarch_result$results$window_method)) {
  stop("Ingarch and Coda base specifications differ")
}
```


Error measure calculations
```{r}

coda_model_error <- model.error(coda_result,fnct = "mse") %>% model.error.overall(fnct = "sum")
ingarch_model_error <- model.error(ingarch_result,fnct = "mse") %>% model.error.overall(fnct = "sum")

coda_model_error
ingarch_model_error

model_error <- rbind(coda_model_error,ingarch_model_error)
                                  
```


```{r}
ps<-ggplot(model_error,aes(x=id,y=error,col=model))+
  geom_point(size=3)+
  theme(text = element_text(size = text_size))+
  ggtitle(paste("Ingarch Timeseries",external_plot,sep=" "),subtitle = paste("Fridge ID:",FID,",base window length:",frame,sep=" "))

if(save_plots){
  ggsave(filename = here("Plots",paste("Fridge_error_measure",paste(unique(model_error$id),collapse="-"),"_ext","_",external,"win_lgth",frame,".png",sep="")),plot=ps,height = 15,width = 20)
}
```


Preparing Data for plotting

```{r}
FID <- 4

plot_data_coda<-coda_result$results%>%
  dplyr::filter(category %in% c(1,2,3,4), id==FID)%>%
  dplyr::select(!c(naive_predicted_value,prediction_error_naive))

all_dates_and_categories<-plot_data_coda[,c("category","prediction_date")]

plot_data_ingarch <- ingarch_result$results %>% dplyr::filter(id==FID)
plot_data_ingarch<-full_join(plot_data_ingarch,all_dates_and_categories)
plot_data_ingarch$model<-"ingarch"

if(one_vs_all) {
  plot_data <-
    bind_rows(plot_data_coda, plot_data_ingarch) %>% dplyr::select(!c(distribution, pivot_group))
} else{
  plot_data <-
    bind_rows(plot_data_coda, plot_data_ingarch) %>% dplyr::select(!c(distribution))
}



```

Show whole timeseries
```{r}
data_raw <- weekly_category_data %>%
          filter(fridge_id == FID&
                   main_category_id %in% c(1, 2, 3, 4)) %>%
          dplyr::select(week_date, main_category_id, sold) %>%
          data.preparation() %>% 
          pivot_longer(cols=c("1","2","3","4"),names_to="category",values_to="true_value")
names(data_raw)[1] <- c("prediction_date")
        
```


Ingarch Timeseries with prediction intervals

```{r}
p<-ggplot(plot_data_ingarch,aes(x=prediction_date,y=predicted_value),col="blue")+
  facet_wrap(vars(category),nrow=length(unique(plot_data_ingarch$category)),scales = "free")+
  geom_point(size=1)+
  geom_ribbon(aes(x=prediction_date,y=predicted_value,ymin=lower_bound,ymax=upper_bound),
              data=plot_data_ingarch,inherit.aes = F,fill="grey90",linetype="dashed",col="blue")+
  geom_line(data=plot_data_ingarch,
            aes(x=prediction_date,y=predicted_value),col="blue")+
  geom_line(data=data_raw,aes(x=prediction_date,y=true_value),col="black",inherit.aes = F)+
  geom_point(data=data_raw,aes(x=prediction_date,y=true_value),col="black",inherit.aes = F)+
  theme(text = element_text(size = text_size))+
  ggtitle(paste("Ingarch Timeseries",external_plot,sep=" "),subtitle = paste("Fridge ID:",FID,",base window length:",frame,sep=" "))

if(save_plots){
  ggsave(filename = here("Plots",paste("ts_ing_id_",FID,"_",distr,"_pi","_ext","_",external,"win_lgth",frame,".png",sep="")),plot=p,height = 15,width = 20)
}

```




Coda Timeseries with prediction intervals
```{r}
p0<-ggplot(plot_data_coda,aes(x=prediction_date,y=predicted_value),col="red")+
  facet_wrap(vars(category),nrow=length(unique(plot_data_coda$category)),scales = "free")+
  geom_point(size=1)+
  geom_ribbon(aes(x=prediction_date,y=predicted_value,ymin=lower_bound,ymax=upper_bound),
              data=plot_data_coda,inherit.aes = F,fill="grey90",linetype="dashed",col="red")+
  geom_line(data=plot_data_coda,
            aes(x=prediction_date,y=predicted_value),col="red")+
  geom_line(data=data_raw,aes(x=prediction_date,y=true_value),col="black",inherit.aes = F)+
  geom_point(data=data_raw,aes(x=prediction_date,y=true_value),col="black",inherit.aes = F)+
  theme(text = element_text(size = text_size))+
  ggtitle(paste("Coda Timeseries",sep=" "),subtitle = paste("Fridge ID:",FID,",base window length:",frame,sep=" "))

if(save_plots){
 ggsave(filename = here("Plots",paste("ts_coda_id_",FID,"_pi","win_lgth",frame,".png",sep="")),plot=p0,height = 15,width = 20) 
}

```

Comparing the timeseries with prediction intervals

```{r}
my_color <- setNames(c("red", "blue"),
                     c("coda","ingarch"))

p1<-ggplot(plot_data,aes(x=prediction_date,y=predicted_value,col=model))+
  facet_wrap(vars(category),nrow=length(unique(plot_data$category)),scales = "free")+
  geom_point(size=1)+
  geom_ribbon(aes(x=prediction_date,y=predicted_value,col=model,ymin=lower_bound,ymax=upper_bound,fill=model),
              data=plot_data,alpha=0.15,inherit.aes = F,linetype="dashed")+
  geom_line(data=plot_data,
            aes(x=prediction_date,y=predicted_value,col=model))+
  geom_line(data=data_raw,aes(x=prediction_date,y=true_value),col="black",inherit.aes = F)+
  geom_point(data=data_raw,aes(x=prediction_date,y=true_value),col="black",inherit.aes = F)+
  scale_color_manual("Legend", values = c(my_color))+
  ggtitle(paste("Actual Timeseries vs. predicted ",sep=" "),subtitle = paste("Fridge ID:",FID,",base window length:",frame,sep=" "))+
  theme(text = element_text(size = text_size))  

if(save_plots){
ggsave(filename = here("Plots",paste("ts_both_id_",FID,"_pi","ing_ext",external,"win_lgth",frame,".png",sep="")),plot=p1,height = 15,width = 20)
  
}
```



Comparing the prediction errors of the models

```{r}
p2<-ggplot(plot_data,aes(x=model,y=prediction_error))+
  facet_wrap(vars(category),ncol=length(unique(plot_data$category)),scales = "fixed")+
  geom_boxplot()+
  ggtitle("Prediction error",subtitle = paste("Fridge ID:",FID,",base window length:",frame,sep=" "))+
  theme(text = element_text(size = text_size))+
  geom_hline(yintercept = 0,col="green")

if(save_plots){
 ggsave(filename = here("Plots",paste("box_pred_err_id",FID,"win_lgth",frame,".png",sep="")),plot=p2,height = 15,width = 20)
 
}
```


Ingarch Parameter / Model Check

```{r eval=FALSE, include=FALSE}

for(category in c(1:4)){
  
  ingarch.parameter.plot(ingarch_result,category=category,element="fitted.values",save=F,plot.type = "default")
  ingarch.parameter.plot(ingarch_result,category=category,element="fitted.values",save=F,plot.type = "histogram")
  
  ingarch.parameter.plot(ingarch_result,category=category,element="fitted.values",save=F,plot.type = "default",func="mean")
  ingarch.parameter.plot(ingarch_result,category=category,element="fitted.values",save=F,plot.type = "histogram",func="mean")
}

```


Normed Prediction errors 
```{r}
p3 <- ggplot(plot_data,aes(x=prediction_date,y=prediction_error_normed,col=model))+
  facet_wrap(vars(category),nrow=length(unique(plot_data$category)),scales = "free")+
  geom_point(size=1.5,aes(shape=model))+
  geom_line()+
  theme(text = element_text(size = text_size))+
  geom_line(aes(y=0),col="black")+
  ggtitle(paste("Normed prediction error over time ",sep=" "),subtitle = paste("Fridge ID:",FID,",base window length:",frame,sep=" "))+
  scale_color_manual("Legend", values = c(my_color))

if(save_plots){
 ggsave(filename = here("Plots",paste("pred_err_norm_id",FID,"win_lgth",frame,".png",sep="")),plot=p3,height = 15,width = 20)
 
}
```



```{r}
p4<-ggplot(plot_data,aes(x=model,y=prediction_error_normed))+
  facet_wrap(vars(category),ncol=length(unique(plot_data$category)),scales = "fixed")+
  geom_boxplot()+
  ggtitle("Normed prediction error per method and category",subtitle = paste("Fridge ID:",FID,",base window length:",frame,sep=" "))+
  theme(text = element_text(size = text_size))+
  geom_hline(yintercept = 0,col="green")

if(save_plots){
 ggsave(filename = here("Plots",paste("box_pred_err_norm_id",FID,"win_lgth",frame,".png",sep="")),plot=p4,height = 15,width = 20)
 
}
```


Lag order of coda model

```{r}

plot_coda_lag <- coda.get.lag(coda_result,id=FID)
p5 <- ggplot(plot_coda_lag, aes(x = window, y = lag)) +
  geom_point(size = 1.5) +
  geom_line() +
  ggtitle(paste("Coda model lag per window", sep = " "),
          subtitle = paste("Fridge ID:", FID,",base window length:",frame, sep = " ")) +
  theme(text = element_text(size = text_size))

if (one_vs_all)
  p5<- p5 + facet_wrap(vars(category), nrow = length(unique((
    plot_coda_lag$category
  ))), scales = "free")

if(save_plots){
ggsave(filename = here("Plots",paste("Coda_lag_id",FID,"win_lgth",frame,".png",sep="")),plot=p5,height = 15,width = 20)
  
}
```


```{r eval=FALSE, include=FALSE}
par(mfrow=c(3,2))
worst_windows <- coda_result$results%>%filter(category%in%c("1","2","3","4"))%>%slice_max(n=3,order_by=abs(prediction_error_normed))%>%dplyr::select(window,category)
best_windows <- coda_result$results%>%filter(category%in%c("1","2","3","4"))%>%slice_min(n=3,order_by=abs(prediction_error_normed))%>%dplyr::select(window,category)

windows <-c(best_windows$window[1:3],worst_windows$window[1:3])
categories <- c(best_windows$category[1:3],worst_windows$category[1:3])
value <- rep(c("best","worst"),each=3)

for(i in 1:6){
plot_coda_det <- coda.get.coefficients(coda_result) %>% filter(window==windows[i],category==categories[i])
plot(plot_coda_det$model_det,main=paste("window",i,value[i]),ylim=c(0,2))
abline(h=1)  
}

```


Prediction error over time
```{r}
p6 <- ggplot(plot_data,aes(x=prediction_date,y=prediction_error,col=model))+
  facet_wrap(vars(category),nrow=length(unique(plot_data$category)),scales = "free")+
  geom_point(size=1.5,aes(shape=model))+
  geom_line()+
  theme(text = element_text(size = text_size))+
  geom_line(aes(y=0),col="black")+
  ggtitle(paste("Prediction error over time ",sep=" "),subtitle = paste("Fridge ID:",FID,",base window length:",frame,sep=" "))+
  scale_color_manual("Legend", values = c(my_color))

if(save_plots){
ggsave(filename = here("Plots",paste("pred_err_id",FID,"win_lgth",frame,".png",sep="")),plot=p6,height = 15,width = 20)
  
}
```

Coda coefficients over windows 
```{r}
plot_coda_det <- coda.get.coefficients(coda_result,fnc="det",id=FID)

p7 <- ggplot(plot_coda_det,aes(x=window,y=value))+
  geom_point(size=1.5)+
  theme(text = element_text(size = text_size))+
  ggtitle(paste("Determinant of the coefficient matrices",sep=" "),subtitle = paste("Fridge ID:",FID,",base window length:",frame,sep=" "))

if (one_vs_all)
  p7<- p7 + facet_wrap(vars(category), nrow = length(unique((
    plot_coda_det$category
  ))), scales = "free")

if(save_plots){
ggsave(filename = here("Plots",paste("coda_det_id",FID,"win_lgth",frame,".png",sep="")),plot=p7,height = 15,width = 20)
  
}
```


Cumulated MSEs 
```{r}
plot_mse_cum <- mse.cumulated(plot_data)
plot_mse_cum$window <- factor(as.character(plot_mse_cum$window),levels=unique(plot_mse_cum$window))


p8 <- ggplot(plot_mse_cum, aes(y=mse_cum,x=window,group=model,col=model))+
  facet_wrap(vars(category),nrow=length(unique(plot_mse_cum$category)),scales = "free")+
  geom_line()+
  geom_point(size=1.5)+
  theme(text = element_text(size = 30),axis.text.x = element_text(angle = 45, vjust = 0.7, hjust=1))+
    ggtitle(paste("Cumulated MSE from right to left",sep=" "),subtitle = paste("Fridge ID:",FID,",base window length:",frame,sep=" "))

p8

if(save_plots){
ggsave(filename = here("Plots",paste("mse_cum",FID,"win_lgth",frame,".png",sep="")),plot=p8,height = 15,width = 20)
  
}
```

